E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-14 System/approach.tex
adding chap3
chap3 prelim edit

\section[Approach]{Our Approach to measure prevalence of E-Mail Header Injection}
\label{sys:appr}
We took a black-box approach to measure the prevalence of E-Mail Header Injection vulnerability on the World Wide Web. Black-box testing \cite{wiki:Black-box_testing} is a way to examine the functionality of an application without looking at its source code.

As we did not have the source code for each of these websites, black-box testing was the ideal approach for this project. Black-box testing allows our system to detect E-Mail Header Injection vulnerabilities in any server-side language (not simply those we identified in Section~\ref{languages}). A high level logical overview of our system is presented in Figure~\ref{fig:overall}. The components shown in Figure~\ref{fig:overall} can be more broadly categorized into different modules, as discussed in the following section.

\begin{figure}
	\centering
	\includegraphics[width=14cm, height=7cm]{System/overall_design}
	\caption[\titlecap{Overall system architecture - logical overview}]{Overall system architecture - logical overview.}
	\label{fig:overall}
\end{figure}

>>>>

\subsection{Approach}
\label{sys:appr}
We took a black-box approach to measure the prevalence of E-Mail Header Injection vulnerability on the World Wide Web. Black-box testing \cite{wiki:Black-box_testing} is a way to examine the functionality of an application without looking at its source code.

As we did not have the source code for each of these websites, black-box testing was the ideal approach for this project. Black-box testing allows our system to detect E-Mail Header Injection vulnerabilities in any server-side language (not simply those we identified in Section~\ref{languages}). The overall architecture of our system is presented in Figure~\ref{fig:overall}. The components shown in Figure~\ref{fig:overall} can be more broadly categorized into different modules, as discussed in the following section.

\begin{figure*}
	\centering
	\includegraphics[width=14cm, height=7cm]{overall}
	\caption{Overall system architecture.}
	\label{fig:overall}
\end{figure*}

### 2016-05-14 System/components.tex
fixed emph
chap3 prelim edit

\subsubsection{Form Parser}
\label{Comp:FP}
The actual pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as method and action. These dictate where we send the HTTP request and what kind of request it is (GET or POST).
	\item Data about the input fields, such as their attributes, names, and default values. The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted.
	\item Headers associated with the page, such as \emph{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow us to reconstruct the forms later for fuzzing, as required.

@@

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain. In our case, this domain was \texttt{wackopicko.com}.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

@@

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
\lstset{language=html}
\begin{enumerate}
	\item
	%inside the lstinline, we need to use \\ for \textbackslash
	\colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems. 
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\nbcc:maluser(xxxx)@wackopicko.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com\\r\\nbcc:maluser(xxxx)@wackopicko.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.

@@

\subsubsection{E-Mail Analyzer}
\label{Comp:EMA}
The E-Mail Analyzer checks for the presence of injected data in the received e-mails. This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
\paragraph{Analyzing regular e-mail}
`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@wackopicko.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@wackopicko.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@wackopicko.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected x-check headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}
\subsubsection{Database}
We collect and store as much data as possible at each stage of the pipeline. This is due to the two following reasons:
\begin{enumerate}
	\item The data is used to validate our findings.
	\item The data collected can be used for other research projects in this area.
\end{enumerate}
Each table in our database is listed in Table~\ref{tab:dbtf} along with the data it is designed to hold. A schema of the database is shown in Figure~\ref{fig:dbschema}.

\begin{table}[!htbp]
	\centering
	\input{System/tables}        
	\caption[\titlecap{Database - tables}]{The different tables in our database.}
	\label{tab:dbtf}
\end{table}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=15cm, height=11cm]{System/dbschema}
	\caption[\titlecap{Database schema}]{Database schema.}
	\label{fig:dbschema}
\end{figure}

>>>>

\subsubsection{Form Parser}
\label{Comp:FP}
The actual pipeline begins at the Form Parser. This module is responsible for parsing the HTML and retrieving data about the forms on the page, including the following:
\begin{itemize}
	\item Form attributes, such as method and action. These dictate where we send the HTTP request and what kind of request it is (GET or POST).
	\item Data about the input fields, such as their attributes, names, and default values. The default values are essential for fields like \colorbox{lightgray}{\lstinline{<input type="hidden">}} as these fields are usually used to check for the submission of forms by bots.
	\item Presence of the \colorbox{lightgray}{\lstinline{<base>}} element in the HTML, as this affects the final URL to which the form is to be submitted.
	\item Headers associated with the page, such as \texttt{referrer}. Once again, these were required to avoid the website from ignoring our system as a bot.
\end{itemize} 
The Form Parser stores all this data in our database, so as to allow us to reconstruct the forms later for fuzzing, as required.

@@

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process \cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system \cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward E-Mail address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

@@

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:
\lstset{language=html}
\begin{enumerate}
	\item
	%inside the lstinline, we need to use \\ for \textbackslash
	\colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com}} - This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com}} - This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems. 
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\nbcc:maluser(xxxx)@example.com\\nx-check:in}} - As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.
	\item \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com\\r\\nbcc:maluser(xxxx)@example.com\\r\\nx-check:in}} - Same as the previous payload, but containing the additional \texttt{\textbackslash{}r} for Windows compatibility.

@@

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received e-mails. This module works on the e-mails received and stored by our Postfix server, and depending on the user who received the e-mail, it performs different functions.
\paragraph{Analyzing regular e-mail}
`Regular e-mail' refers to the e-mails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this e-mail is identify if the input fields that we injected with data appear on the resulting e-mail, and if so, which fields appear where.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected bcc headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected x-check headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

### 2016-05-14 System/sys_arch.tex
chap3 added
chap3 prelim edit

\section{System Architecture}
\label{sys:arch}
The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
\begin{enumerate}
	\item Data Gathering\\
	The Data Gathering module (shown in Figure~\ref{fig:crawler}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section \ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section \ref{Comp:FP}).
		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section \ref{Comp:EMFC}).
	\end{itemize} 
	\item Payload Injection\\
	The Payload Injection module (shown in Figure~\ref{fig:fuzzer}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section \ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section \ref{Comp:Fuzzer:nmp}).
		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section \ref{Comp:EMA}).
		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section \ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
\end{enumerate}

\begin{figure}
	\centering
	\includegraphics[width=14cm, height=7cm]{System/crawler_design}
	\caption[\titlecap{System architecture - crawler}]{System architecture - crawler \& form parser.}
	\label{fig:crawler}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=16cm, height=9cm]{System/fuzzer_design}
	\caption[\titlecap{System architecture - fuzzer {\&} e-mail analyzer}]{System architecture - fuzzer {\&} e-mail analyzer.}
	\label{fig:fuzzer}
\end{figure}

>>>>

\subsection{System Architecture}
\label{sys:arch}
The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
\begin{enumerate}
	\item Data Gathering\\
	The Data Gathering module (shown in Figure~\ref{fig:crawler}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section \ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section \ref{Comp:FP}).
		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section \ref{Comp:EMFC}).
	\end{itemize} 
	\item Payload Injection\\
	The Payload Injection module (shown in Figure~\ref{fig:fuzzer}) is primarily responsible for the following activities:
	\begin{itemize}
		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section \ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section \ref{Comp:Fuzzer:nmp}).
		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section \ref{Comp:EMA}).
		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section \ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
\end{enumerate}
